Perceptions and Preferences for Meritocracy Scale (PPM-S)

### 2020-01-10 index.Rmd
update1001-2020

```{r eval=FALSE, echo=FALSE}
# Para obtener doble output (html/pdf) correr directamente en consola/terminal:
rmarkdown::render('index.rmd', output_format = 'all')
```

>>>>

```{r eval=FALSE, echo=FALSE}
# Para obtener doble output (html/pdf) correr directamente en consola/terminal:
rmarkdown::render('production/index.rmd', output_format = 'all',output_dir = ".")
```
